---
title: "Dean's Dilemma"
author: "Parv Patni"
date: "December 10, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## TASK 2b - Reading the dataset

```{r}
getwd()
dean.df<-read.csv(paste("Data - Deans Dilemma.csv",sep=""))
head(dean.df)
```
## TASK 2c - Summarize the dataset

```{r}
library(psych)
describe(dean.df)
```

## TASK 3a
calculate the median salary of all the students in the data sample

```{r}
median(dean.df$Salary)
```

## TASK 3b
calculate the percentage of students who were placed, correct to 2 decimal places.

```{r}
a<-round(prop.table(table(dean.df$Placement))*100, digits = 2)
a[2]
```


## TASK 3c
create a dataframe called placed, that contains a subset of only those students who were successfully placed. 

```{r}
placed <- dean.df[which(dean.df$Placement_B == 1),]
```

##TASK 3d
find the  median salary of students who were placed.

```{r}
median(placed$Salary)
```

##TASK 3e
create a table showing the mean salary of males and females, who were placed. 

```{r}
aggregate(placed$Salary, by=list(gender = placed$Gender), mean)
```

##TASK 3f
generate histogram showing a breakup of the MBA performance of the students who were placed

```{r}
hist(placed$Percent_MBA, breaks = 2, ylab = "count", xlab="MBA Pe.rcentage", main="MBA performence of placed students", col=c("lightgreen", "yellow", "pink"))
```
##TASK 3g
Create a dataframe called notplaced, that contains a subset of only those students who were NOT placed after their MBA.

```{r}
notplaced=dean.df[which(dean.df$Placement_B==0),]
```

##TASK 3h
Draw two histograms side-by-side, visually comparing the MBA performance of Placed and Not Placed students, as follows:

```{r}
par(mfrow=c(1,2))
with(placed, hist(placed$Percent_MBA, main = "Placed students",xlab = "MBA percentage",ylab="count", breaks = 2, col = "yellow"))
with(notplaced, hist(notplaced$Percent_MBA, main = "Placed students",xlab = "MBA percentage",ylab="count", breaks = 2, col = "skyblue"))
```
##TASK 3i
draw two boxplots, one below the other, comparing the distribution of salaries of males and females who were placed, as follows:

```{r}
boxplot(placed$Salary ~ placed$Gender, main="Comparison of Salaries of Males and Females",
              col=c("yellow"),horizontal=TRUE,
              xlab="Salary", ylab = "Gender" )
```

## TASK 3j
Create a dataframe called placedET, representing students who were placed after the MBA and who also gave some MBA entrance test before admission into the MBA program.  

```{r}
placedET<- dean.df[which(dean.df$S.TEST==1 & dean.df$Placement_B==1),]
```
##TASK 3k
Draw a Scatter Plot Matrix for 3 variables -- {Salary, Percent_MBA, Percentile_ET} using the dataframe placedET.

```{r}
library(car)
scatterplotMatrix(formula = ~ Salary + Percent_MBA + Percentile_ET, data = placedET, main = "Scatter Plot Matrix")
```