---
title: "T-test (Dean's Dilemma)"
author: "Parv Patni"
date: "December 12, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
getwd()
df <- read.csv("Data - Deans Dilemma.csv")
```
## Task 3b
```{r}
placed<-df[which(df$Placement_B==1),]
(aggregate(df$Salary~df$Gender, data=placed, FUN=mean))
```
average salary of male MBAs who were placed - 284241.9 

average salary of female MBAs who were placed - 253068.0 
```{r}
boxplot(placed$Salary~placed$Gender,main = "Average Salary of Male MBAs and Female MBAs", horizontal = TRUE, ylab = "Gender (Male/Female)", xlab = "Salary" ,col = (c("yellow","skyblue")), ylab = "Average Salary")
```

Since , the average salaries of males is higher than the average salaries of females in this dataset , their is a significant Gender Gap .

## Task 3c
Let us consider this Null Hypothesis :The is no significant difference between the average salary of male MBAs and female MBAs 
```{r}
t.test(Salary ~ Gender , data = placed)
```
The p-value is 0.0023 which is less than 0.05. Hence, we can safely reject the null hypothesis. This implies that there is a significant difference between average salaries of males and females i.e the average salary of the male MBAs is higher than the average salary of female MBAs.